---
title: "Cleaning the Data"
author: "Hayaku"
date: "03/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(tidyverse)
library(unglue)
```

# Research Question No. 4

What are the recurring patterns of policy responses across different countries in the world and how has it impacted the consumption of alcohol?

## Reading in Data

### Reading in Data of Policy Responses Worldwide

This section contains the code to read in data of policy responses to the problem of alcoholism from different parts of the world for the years 2010-2016.

```{r}
file_path <- ("../data/{geo}/")
csv_africa_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("africa"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))
csv_asia_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("asia"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))
csv_americas_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("americas"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))
csv_europe_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("europe"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))
csv_med_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("med"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))
csv_pacific_paths <- glue::glue(file_path, "{geo}_{alpha}.csv", 
                        geo = c("pacific"), 
                        alpha = c("2010", "2011", "2012","2013","2014","2015","2016"))

africa_2010 <- read_csv(csv_africa_paths[1])
africa_2011 <- read_csv(csv_africa_paths[2])
africa_2012 <- read_csv(csv_africa_paths[3])
africa_2013 <- read_csv(csv_africa_paths[4])
africa_2014 <- read_csv(csv_africa_paths[5])
africa_2015 <- read_csv(csv_africa_paths[6])
africa_2016 <- read_csv(csv_africa_paths[7])

americas_2010 <- read_csv(csv_americas_paths[1])
americas_2011 <- read_csv(csv_americas_paths[2])
americas_2012 <- read_csv(csv_americas_paths[3])
americas_2013 <- read_csv(csv_americas_paths[4])
americas_2014 <- read_csv(csv_americas_paths[5])
americas_2015 <- read_csv(csv_americas_paths[6])
americas_2016 <- read_csv(csv_americas_paths[7])

europe_2010 <- read_csv(csv_europe_paths[1])
europe_2011 <- read_csv(csv_europe_paths[2])
europe_2012 <- read_csv(csv_europe_paths[3])
europe_2013 <- read_csv(csv_europe_paths[4])
europe_2014 <- read_csv(csv_europe_paths[5])
europe_2015 <- read_csv(csv_europe_paths[6])
europe_2016 <- read_csv(csv_europe_paths[7])

asia_2010 <- read_csv(csv_asia_paths[1])
asia_2011 <- read_csv(csv_asia_paths[2])
asia_2012 <- read_csv(csv_asia_paths[3])
asia_2013 <- read_csv(csv_asia_paths[4])
asia_2014 <- read_csv(csv_asia_paths[5])
asia_2015 <- read_csv(csv_asia_paths[6])
asia_2016 <- read_csv(csv_asia_paths[7])

med_2010 <- read_csv(csv_med_paths[1])
med_2011 <- read_csv(csv_med_paths[2])
med_2012 <- read_csv(csv_med_paths[3])
med_2013 <- read_csv(csv_med_paths[4])
med_2014 <- read_csv(csv_med_paths[5])
med_2015 <- read_csv(csv_med_paths[6])
med_2016 <- read_csv(csv_med_paths[7])

pacific_2010 <- read_csv(csv_pacific_paths[1])
pacific_2011 <- read_csv(csv_pacific_paths[2])
pacific_2012 <- read_csv(csv_pacific_paths[3])
pacific_2013 <- read_csv(csv_pacific_paths[4])
pacific_2014 <- read_csv(csv_pacific_paths[5])
pacific_2015 <- read_csv(csv_pacific_paths[6])
pacific_2016 <- read_csv(csv_pacific_paths[7])
```

### Reading in Data Required to Check Consumption of Alcohol

This section contains the code to read in data which will help track worldwide consumption of alcohol

```{r}
consumption_pattern <- read_csv("../data/consumption_pattern.csv")
```

## Cleaning the data

### Cleaning Data Pertaining to Policy Responses


