---
title: "Youth and Alcohol"
author: "Kexin Xu"
date: "2021/5/3"
output: html_document
---

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Research Question No. 5

**Do drinking age restrictions and legal blood alcohol concentration (BAC) limits for young drivers have any effect on adolescents’ drinking among countries?**

_Researcher: Kexin Xu_

## Description of Data
All data sets below are downloaded from [**Global Information System on Alcohol and Health (GISAH)**](https://apps.who.int/gho/data/node.gisah.GISAH?showonly=GISAH) in WHO.  

1. BAC limits
  - The data describes legal blood alcohol concentration (BAC) limits for young/novice drivers.
  - The data contains BAC restrictions in each country in year 2016.

2. Age limits
  - The data shows age limits for both alcohol sales and alcohol service.
  - The data contains age restrictions on selling and serving different types of alcohol in each country in year 2016.
  
3. Current drinkers 15-19
  - The data tells the percentage of current drinkers between 15 and 19 years old.
  - The data is consist of percentage of current young drinkers across gender in each country in year 2016.

4. Heavy drinkers 15-19
  - The data represents the percentage of heavy episodic drinkers among drinkers between 15 and 19 years old.
  - The data is consist of percentage of heavy drinkers among young drinkers across gender in each country in year 2016.

## Reading in Data
```{r}
BAC_limits_raw <- read_csv(here::here("data/Legal_blood_alcohol_concentration_(BAC)_limits_for_youngnovice_drivers.csv"))
```

```{r}
Age_limits_raw <- read_csv(here::here("data/Age_limits_Alcohol_servicesales.csv"))
```

```{r}
current_drinkers_15_19_raw <- read_csv(here::here("data/15-19_years_old_current_drinkers_(%).csv"))
```

```{r}
heavy_drinkers_15_19_raw <- read_csv(here::here("data/15-19_years_old_heavy_episodic_drinking_drinkers_only_past_30_days.csv"))
```


## Cleaning the Data
```{r}
BAC_limits_tidy <- BAC_limits_raw[-1,] %>% 
  rename("country" = X1, 
         "year" = X2, 
         "BAC_limits" = 'Legal blood alcohol concentration (BAC) limits') %>% 
  filter(!(BAC_limits == "."))
```

```{r}
Age_limits_tidy <- Age_limits_raw[-1,] %>% 
   rename("country" = X1, 
          "year" = X2, 
          "sale_beer" = 'Age limits off-premise sales',
          "sale_wine" = 'Age limits off-premise sales_1',
          "sale_spirits" = 'Age limits off-premise sales_2',
          "service_beer" = 'Age limits on-premise service',
          "service_wine" = 'Age limits on-premise service_1',
          "service_spirits" = 'Age limits on-premise service_2') %>%
  pivot_longer(cols = c(-country, -year), names_to = "type", values_to = "limit")
```

```{r}
current_drinkers_15_19_tidy <- current_drinkers_15_19_raw[-1,] %>% 
  rename("country" = X1, 
          "year" = X2, 
          "All" = '15-19 years old, current drinkers (%)',
          "Male" = '15-19 years old, current drinkers (%)_1',
          "Female" = '15-19 years old, current drinkers (%)_2') %>% 
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage") %>% 
  separate(col = percentage, into = c("drinker_percentage", "range"), " ")
current_drinkers_15_19_tidy <- current_drinkers_15_19_tidy[,-5]
```

```{r}
heavy_drinkers_15_19_tidy <- heavy_drinkers_15_19_raw[-1,] %>% 
  rename("country" = X1, 
          "year" = X2, 
          "All" = 'Heavy episodic drinking (youth 15 -19 years), drinkers only, past 30 days (%)',
          "Male" = 'Heavy episodic drinking (youth 15 -19 years), drinkers only, past 30 days (%)_1',
          "Female" = 'Heavy episodic drinking (youth 15 -19 years), drinkers only, past 30 days (%)_2') %>% 
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage") %>% 
  separate(col = percentage, into = c("heavy_drinker_percentage", "range"), " ")
heavy_drinkers_15_19_tidy <- heavy_drinkers_15_19_tidy[,-5]
```

## Storing Cleaned Data Set
```{r}
write_csv(BAC_limits_tidy, "../clean_data/BAC_limits_tidy.csv")
```

```{r}
write_csv(Age_limits_tidy, "../clean_data/Age_limits_tidy.csv")
```

```{r}
write_csv(current_drinkers_15_19_tidy, "../clean_data/current_drinkers_15_19_tidy.csv")
```

```{r}
write_csv(heavy_drinkers_15_19_tidy, "../clean_data/heavy_drinkers_15_19_tidy.csv")
```



# Research Question No. 6

**What are the trends in youth drinking issues over the years?**

_Researcher: Kexin Xu_

## Description of Data
All data sets below are downloaded from [**Global Information System on Alcohol and Health (GISAH)**](https://apps.who.int/gho/data/node.gisah.GISAH?showonly=GISAH) in WHO.  
Age of 15 is taken on behalf of youth here. The following data sets describe different drinking issues based on 15-year-old teenagers.  

1. Drink at least once a week
  - The data shows the percentage of whom has any alcoholic beverage at least once a week.
  - The data contains the percentage of 15-year-old adolescents who drinks alcoholic beverage at least once a week across gender in each country in different years.

2. First drink earlier than 13
  - The data describes the percentage of whose first drink at 13 years old or younger.
  - The data contains the percentage of 15-year-old adolescents who first drinks alcoholic beverage earlier than 13 across gender in each country in different years.
  
3. Any alcohol in past 12 months
  - The data represents the percentage of whom has any alcohol in past 12 months.
  - The data is consist of percentage of 15-year-old adolescents who any alcoholic beverage in the past year across gender in each country in different years.

4. Any alcohol in past 30 days
  - The data represents the percentage of whom has any alcohol in past 30 days.
  - The data is consist of percentage of 15-year-old adolescents who any alcoholic beverage in the past month across gender in each country in different years.

## Reading in Data
```{r}
at_least_once_a_week_raw <- read_csv(here::here("data/15_years_old_any_alcoholic_beverage_at_least_once_a_week_(%).csv"))
```

```{r}
first_drink_earlier_than_13_raw <- read_csv(here::here("data/15_years_old_first_drink_at_13_years_or_younger_(%).csv"))
```

```{r}
any_alcohol_in_past_12_months_raw <- read_csv(here::here("data/15_years_old_any_alcoholic_beverage_in_past_12_months_(%).csv"))
```

```{r}
any_alcohol_in_past_30_days_raw <- read_csv(here::here("data/15_years_old_any_alcoholic_beverage_in_past_30_days_(%).csv"))
```

## Cleaning the Data
```{r}
at_least_once_a_week_tidy <- at_least_once_a_week_raw[-1,-2] %>% 
  rename("country" = X1, 
          "year" = X3, 
          "Male" = '15-years old, any alcoholic beverage consumed at least once a week, (%)',
          "Female" = '15-years old, any alcoholic beverage consumed at least once a week, (%)_1') %>%
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage")
```

```{r}
first_drink_earlier_than_13_tidy <- first_drink_earlier_than_13_raw[-1,-2] %>% 
  rename("country" = X1, 
          "year" = X3, 
          "All" = '15-years old first drink at 13 years or younger, (%)',
          "Male" = '15-years old first drink at 13 years or younger, (%)_1',
          "Female" = '15-years old first drink at 13 years or younger, (%)_2') %>%
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage")
```

```{r}
any_alcohol_in_past_12_months_tidy <- any_alcohol_in_past_12_months_raw[-1,-2] %>% 
  rename("country" = X1, 
          "year" = X3, 
          "All" = '15-years old any alcoholic beverage consumed in past 12 months, (%)',
          "Male" = '15-years old any alcoholic beverage consumed in past 12 months, (%)_1',
          "Female" = '15-years old any alcoholic beverage consumed in past 12 months, (%)_2') %>%
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage")
```

```{r}
any_alcohol_in_past_30_days_tidy <- any_alcohol_in_past_30_days_raw[-1,-2] %>% 
  rename("country" = X1, 
          "year" = X3, 
          "All" = '15-years old any alcoholic beverage consumed in past 30 days, (%)',
          "Male" = '15-years old any alcoholic beverage consumed in past 30 days, (%)_1',
          "Female" = '15-years old any alcoholic beverage consumed in past 30 days, (%)_2') %>%
  pivot_longer(cols = c(-country, -year), names_to = "gender", values_to = "percentage")
```

## Storing Cleaned Data Set
```{r}
write_csv(at_least_once_a_week_tidy, "../clean_data/at_least_once_a_week_tidy.csv")
```

```{r}
write_csv(first_drink_earlier_than_13_tidy, "../clean_data/first_drink_earlier_than_13_tidy.csv")
```

```{r}
write_csv(any_alcohol_in_past_12_months_tidy, "../clean_data/any_alcohol_in_past_12_months_tidy.csv")
```

```{r}
write_csv(any_alcohol_in_past_30_days_tidy, "../clean_data/any_alcohol_in_past_30_days_tidy.csv")
```




