---
title: "Alcohol Consumption Patterns"
output:
  flexdashboard::flex_dashboard:
    theme: bootstrap
    vertical_layout: scroll
runtime: shiny
---
   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(maps)
library(plotly)
library(flexdashboard)
library(kableExtra)
library(leaflet)
library(stringr)
```

Introduction {.tabset}
======================

Column {.tabset} {data-width=800}
-------------------------------------

### Background




Column {.tabset} {data-width=200}
-------------------------------------

### Approach of Project

The report will be collating specific sections of this data pertaining to countrywise policy responses, consumption pattern, youth and alcohol, levels of consumption and harms and consequences.

### Information on Data

This report is being created using the data from the GISAH (Global Information System on Alcohol and Health) tool of the World Health Organisation. GISAH tool helps monitor trends relating to alcohol consumption across various age groups, side effects (harm caused) as well as the policy responses by different countries.

### Makers

**Team Name: Hayaku**

_Researchers:_

- _Kexin Xu_
- _Smriti Vinayak Bhat_
- _Yalong liu_
- _Yin Shan Ho_


Popularity {.tabset} 
======================


Cause of Mortality {.tabset} 
======================

Policy Pattern {.tabset}
======================

Column {.tabset} {data-width = 400}
------------------------
### Infographic of Policies

```{r read_data}
policy_pattern <- read_csv("../clean_data/policy_pattern.csv")
consumption_pattern <- read_csv("../clean_data/consumption_pattern.csv")
```

```{r}

policy_country_group <- policy_pattern %>%
  pivot_longer(cols = c("2010", "2011", "2012", "2013", "2014","2015", "2016"),
               names_to = "Year",
               values_to = "Action")

cities <- data.frame(world.cities) %>%
  filter(capital == 1)

world <- map_data("world") %>%
  mutate(Country = region) %>%
  select(long,lat,region)

policy_country_group_map <- policy_country_group %>%
  left_join(cities, by = c("Country" = "country.etc")) %>%
  na.omit() %>%
  select(Country,`Action Area`,Action,lat,long,name,Year)
```

```{r}
ui <- bootstrapPage(tags$style(type = "text/css", "html, body, .leaflet {width:100%; height:100%}"),
                    leafletOutput("map", width = "100%", height = "100%"),
                    # position and properties of the time slider
                    absolutePanel(top = 10, right = 10, draggable = TRUE,
                                  # slider title, step increments, and ticks
                                  sliderInput("integer", "Year", min = 2010, max = 2016, value = 2010, step = 1,ticks = FALSE, width = '100px', sep = "",
                                              animate =
                                                  animationOptions(interval = 4000, loop = TRUE))))

# shiny server input/output
server <- function(input, output, session) {
    filteredData <- reactive({
        policy_country_group_map %>%
            filter(Year == input$integer)
    })
    output$map <- renderLeaflet({
        leaflet(world) %>%
            addProviderTiles(providers$CartoDB.Positron) %>%
            # set boundaries for map
            fitBounds(lng1 = min(world$long),
                      lat1 = min(world$lat),
                      lng2 = max(world$long),
                      lat2 = max(world$lat))
    })
    observe({
        leafletProxy("map", data = filteredData()) %>%
            clearMarkers() %>%
            addMarkers(~long, ~lat, popup = ~as.character(Action), label = ~as.character(`Action Area`))
    })
}
shinyApp(ui=ui, server=server, options = list(height = 500), enableBookmarking = "server")
```


### Effectiveness of Policy Actions

```{r}
consumption_pattern_filter <- consumption_pattern %>%
  filter(`Beverage Types` == "All types") %>%
  select(-`Beverage Types`) %>%
  pivot_longer(cols = -c("Country"), names_to = "Year", values_to = "Per Capita Alcohol Consumed") %>%
  left_join(policy_country_group) %>%
  filter(`Per Capita Alcohol Consumed` > 0) %>%
  group_by(Country) %>%
  arrange(Year, .by_group = TRUE)

df <- data.frame(row_no=numeric())
consumption_pattern_filter$row_no <- seq.int(nrow(consumption_pattern_filter)) 

finaltbl <- consumption_pattern_filter %>%
  na.omit() %>%
  mutate(row_no2 = row_no + 1)

addtbl <- finaltbl %>%
  select(row_no2) %>%
  left_join(consumption_pattern_filter) %>%
  filter(row_no == row_no2) %>%
  select(-c(row_no,row_no2))

finaltbl <- finaltbl %>%
  select(-c(row_no,row_no2))
  

tbl1 <- rbind(addtbl,finaltbl) %>%
  arrange(Country, Year)

tbl <- tbl1 %>%
  distinct(`Per Capita Alcohol Consumed`, .keep_all = TRUE) %>%
  select(Year, `Per Capita Alcohol Consumed`)

```



```{r}

lag_tbl <- lag(tbl) %>%
  select(Country, Year, `Per Capita Alcohol Consumed`) %>%
  mutate(alc_diff = `Per Capita Alcohol Consumed`) %>%
  cbind(tbl) %>%
   transmute(Country = Country...5, Year = Year...6, `Per Capita Alcohol Consumed` = `Per Capita Alcohol Consumed...7`,alc_diff = alc_diff)
 for (i in 1:452) {
   ifelse(lag_tbl$Country[i] == lag_tbl$Country[i+1],
          next,
          lag_tbl$alc_diff[i+1] <- NA)
 }
lag_tbl <- lag_tbl %>%
  mutate(Year = as.numeric(Year)-1)

lag_tbl <- lag_tbl %>%
   mutate(alc_diff_2= `Per Capita Alcohol Consumed` - alc_diff) %>%
   filter(!is.na(alc_diff_2)) %>%
   mutate(Trend = ifelse(alc_diff_2<=0,"Reducing","Increasing"))

tbl1 <- tbl1 %>%
  mutate(Year = as.numeric(Year)) %>%
  select(-`Per Capita Alcohol Consumed`)

check_tbl <- full_join(lag_tbl,tbl1) %>%
  arrange(Country, Year) %>%
  na.omit() %>%
  unique()

fin_tbl <- check_tbl %>%
   group_by(Year,`Action Area`, Trend) %>%
   tally() %>%
  mutate(Year = as.character(Year))

p2 <- fin_tbl %>%
  ggplot(aes(y = Year, x= n,fill = Trend)) +
  facet_wrap(~`Action Area`, labeller = labeller(`Action Area` = label_wrap_gen(70)), ncol = 2) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(strip.background = element_rect(colour = "white", fill = "white"), strip.text.x = element_text(size=6, color = "black", face = "bold"), axis.text.y = element_text(angle = 5, hjust = 1, size = 6), axis.title.x = element_text(size=9)) +
  labs(x = "Number of Countries")

ggplotly(p2)
```



Column {.tabset} {data-width = 650}
------------------------------------

### Policies being favored by countries across years 2010-2016

```{r}
policy_country_group_plot <- check_tbl %>%
  na.omit() %>%
  group_by(`Action Area`,Year) %>%
  tally() %>%
  arrange(Year)


p <- policy_country_group_plot %>%
  ggplot(aes(x=Year,y=n, group = `Action Area`)) +
  geom_line(aes(color = `Action Area`)) +
  geom_point() +
  labs(y = "Number of Countries") +
  theme_bw() +
  theme(legend.position = "left", legend.text = element_text(size = 7)) 
ggplotly(p) %>%
  layout(legend = list(x = 0,
                     y = 1,
                     tracegroupgap = 0))
```



### Analysis

```{r}
act_area <-  length(unique(policy_country_group$`Action Area`))
```

- There are `r act_area` main areas of Policy Actions that the effectiveness are measured for.
From the figure of Policies favored across countries from the years 2010-2016, it is visible that 'Leadership, awareness and commitment' policies are the ones that are being favored by most countries.
```{r}
df <- check_tbl %>%
  arrange(alc_diff_2)
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally() %>%
  length()
```

- Upon checking the largest decreases in per capita alcohol consumption it is visible that this policy has only `r df` entry.
```{r}
df <- check_tbl %>%
  arrange(desc(alc_diff_2))
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally()
```

- However upon checking the largest increases in per capita alcohol consumption it is visible that this policy has `r df[1]` entries.
- This shows that the governments of the different countries may not be taking the most efficient of routes.
```{r}
df <- check_tbl %>%
  group_by(`Action Area`) %>%
  summarise(mean = mean(alc_diff_2)) %>%
  arrange(mean)

kbl(df) %>%
  kable_minimal(font_size = 9) %>%
  row_spec(1, bold = T) %>%
  row_spec(10, bold = T)
```
- From the table we can see that the most efficient action area seems to be - `r paste(df$'Action Area'[1])`
- While the least efficient area is - `r paste(df$'Action Area'[10])`
- One area of relief is that the second most efficent action area i.e., `r paste(df$'Action Area'[2])`, is also the second most used strategy by countries across the world.
```{r}
df1 <- check_tbl %>%
  filter(alc_diff_2 == min(alc_diff_2))
df2 <- check_tbl %>%
  filter(alc_diff_2 == max(alc_diff_2))
```

> The biggest dip in consumption was seen in `r paste(df1$Country[1])` in the year `r paste(df1$Year[1])` after the step - `r paste(df1$Action[1])`.

> The biggest spike in consumption was seen in `r paste(df2$Country[1])` in the year `r paste(df2$Year[1])` after the step - `r paste(df2$Action[1])`

-------------------
Age Restrictions {.tabset}
======================



Youth Inebriation {.tabset}
======================


Limitations {.tabset}
======================

### Policy Patterns

1. The values for each policy area have not been weighted by importance.
2. Data is not available for a large number of countries so the analysis has been performed on the limited data set given.
3. This analysis has only been limited between the years of 2010-2016.
4. There could be population/age bias as demographic data is unavailable.

References {.tabset}
======================

GHO | global information system on alcohol and Health (gisah) | global information system on alcohol and health. (n.d.). Retrieved May 09, 2021, from https://apps.who.int/gho/data/node.gisah.GISAH?lang=en&amp;showonly=GISAH