---
title: "Alcohol Consumption Patterns"
output:
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: columns
    vertical_layout: scroll
    runtime: shiny
---
   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(tidyverse)
library(dplyr)
library(maps)
library(plotly)
library(flexdashboard)
library(kableExtra)
library(rnaturalearth)
library(RColorBrewer)
library(sf)
library(viridis)
library(leaflet)
library(stringr)
library(shiny)
library(gridExtra)
library(ggiraph)
library(tidytuesdayR)
library(gganimate)
library(ggplot2)
library(naniar)
```

Introduction {.tabset}
======================

Column {.tabset} {data-width=800}
-------------------------------------

### Background




Column {.tabset} {data-width=200}
-------------------------------------

   
### Approach of Project

The report will be collating specific sections of this data pertaining to countrywise policy responses, consumption pattern, youth and alcohol, levels of consumption and harms and consequences.

### Information on Data

This report is being created using the data from the GISAH (Global Information System on Alcohol and Health) tool of the World Health Organisation. GISAH tool helps monitor trends relating to alcohol consumption across various age groups, side effects (harm caused) as well as the policy responses by different countries.

### Makers

**Team Name: Hayaku**

_Researchers:_

- _Kexin Xu_
- _Smriti Vinayak Bhat_
- _Yalong liu_
- _Yin Shan Ho_


Popularity General {.tabset}
======================

Column {data-width=500}
-------------------------------------

### Popular changes in beer

```{r}
consumption <- read_csv("../clean_data/consumption_join.csv")

consumption[consumption == 0] <- NA
```

```{r}
# Pivoting Beverage_Types and Year

c_tidy <- consumption %>%
  pivot_longer(cols = -c(Country, Beverage_Types),
               names_to = "Year",
               values_to = "Litres") %>%
  mutate(Beverage_Types = recode(Beverage_Types,
                                 "All types" = "All_types",
                                 "Other alcoholic beverages" = "Other_alcoholic_beverages")) %>%
  pivot_wider(names_from = Beverage_Types,
              values_from = Litres) %>%
  mutate(All_types = as.double(as.character(All_types))) %>%
  mutate(Beer = as.double(as.character(Beer))) %>% 
  mutate(Wine = as.double(as.character(Wine))) %>% 
  mutate(Spirits = as.double(as.character(Spirits))) %>% 
  mutate(Other_alcoholic_beverages = as.double(as.character(Other_alcoholic_beverages))) 
```

```{r}
# Loading countries data

countries <- ne_countries(returnclass = "sf", scale = "medium") %>%
  select(admin, continent, pop_est, gdp_md_est, economy, income_grp )
```

```{r}
# Test unmatched countries

country_test <- anti_join(c_tidy, countries, by = c("Country" = "admin"))

# Modify the country name consisting with rnaturalearth package

c_tidy <- c_tidy %>%
  mutate(Country = recode(Country,
                             "Bahamas" = "The Bahamas",
                             "Bolivia (Plurinational State of)" = "Bolivia",
                             "Brunei Darussalam" = "Brunei",
                             "Cabo Verde" = "Cape Verde",
                             "Congo" = "Democratic Republic of the Congo",
                             "Côte d'Ivoire" = "Ivory Coast",
                             "Czechia" = "Czech Republic",
                             "Democratic People's Republic of Korea" = "North Korea",
                             "Eswatini" = "Swaziland",
                             "Guinea-Bissau" = "Guinea Bissau",
                             "Iran (Islamic Republic of)" = "Iran",
                             "Lao People's Democratic Republic" = "Laos",
                             "Micronesia (Federated States of)" = "Federated States of Micronesia",
                             "North Macedonia" = "Macedonia",
                             "Republic of Korea" = "South Korea",
                             "Republic of Moldova" = "Moldova",
                             "Russian Federation" = "Russia",
                             "Serbia" = "Republic of Serbia",
                             "Syrian Arab Republic" = "Syria",
                             "Timor-Leste" = "East Timor",
                             "Tuvalu" = "Wallis and Futuna",
                             "United Kingdom of Great Britain and Northern Ireland" = "United Kingdom", 
                             "Venezuela (Bolivarian Republic of)" = "Venezuela",
                             "Viet Nam" = "Vietnam"))
```

```{r}
# Beer data

beer_data <- c_tidy %>%
  select(Country, Year, Beer)

# Beer popularity by time

beer_time <- left_join(countries, beer_data, by = c("admin" = "Country"))

  b_time  <- ggplot() +
  geom_sf(data = countries, fill = NA) +
  geom_sf(data = beer_time %>% 
  filter(!is.na(Year)), mapping = aes(fill = Beer)) +
  scale_fill_gradient(low = "#1e5a85", high = "#a2e951",
    space = "Lab", na.value="white", guide = "colourbar",
    aesthetics = "fill") +
  labs(title = "Countries where Beer is popular",
       subtitle = "Year: {current_frame}",
       fill = "Total") +
  theme_void() +
  theme(legend.position = "bottom") +
  transition_manual(Year)

  animate(b_time, duration = 30, fps = 20, width = 1000, 
          height = 500, renderer = gifski_renderer())
```


### Beer

```{r}
# Test unmatched countries

countrys_test <- anti_join(consumption, countries, by = c("Country" = "admin"))

# Modify the country name consisting with rnaturalearth package

consumption_c <- consumption %>%
  mutate(Country = recode(Country,
                             "Bahamas" = "The Bahamas",
                             "Bolivia (Plurinational State of)" = "Bolivia",
                             "Brunei Darussalam" = "Brunei",
                             "Cabo Verde" = "Cape Verde",
                             "Congo" = "Democratic Republic of the Congo",
                             "Côte d'Ivoire" = "Ivory Coast",
                             "Czechia" = "Czech Republic",
                             "Democratic People's Republic of Korea" = "North Korea",
                             "Eswatini" = "Swaziland",
                             "Guinea-Bissau" = "Guinea Bissau",
                             "Iran (Islamic Republic of)" = "Iran",
                             "Lao People's Democratic Republic" = "Laos",
                             "Micronesia (Federated States of)" = "Federated States of Micronesia",
                             "North Macedonia" = "Macedonia",
                             "Republic of Korea" = "South Korea",
                             "Republic of Moldova" = "Moldova",
                             "Russian Federation" = "Russia",
                             "Serbia" = "Republic of Serbia",
                             "Syrian Arab Republic" = "Syria",
                             "Timor-Leste" = "East Timor",
                             "Tuvalu" = "Wallis and Futuna",
                             "United Kingdom of Great Britain and Northern Ireland" = "United Kingdom", 
                             "Venezuela (Bolivarian Republic of)" = "Venezuela",
                             "Viet Nam" = "Vietnam"))
```


```{r}
# Percentage of change

b_percent <- consumption_c %>%
  filter(Beverage_Types == "Beer") %>%
  select("Country", "2018", "1965") %>%
  na.omit() %>%
  mutate("Percent" = (b_percent$"2018" - b_percent$"1965")) 
b_percent
```



```{r}
beer_time <- left_join(countries, b_percent, by = c("admin" = "Country"))
ggplot()+
  geom_sf(data = beer_time, mapping = aes(fill = Percent)) +
  scale_fill_distiller(palette = "Spectral", na.value = "white", ) +
    labs(title = "Beer",
       fill = "") +
    theme_void()+
  theme(panel.grid.major = element_line(colour = "transparent"),
        legend.position = "bottom")

```






### Spirits

```{r}
# Percentage of change

s_data <- consumption_c %>%
  filter(Beverage_Types == "Spirits") %>%
  select("Country", "2018", "1965") %>%
  na.omit() %>%
  group_by(Country) %>%
  mutate("Deviation" = (s_data$"2018" - s_data$"1965"))
s_data
```


Column {data-width=500}
-------------------------------------

### Consumption trends of each type of alcohol

```{r}
trend_total <- c_tidy %>%
  pivot_longer(cols = -c(Country, Year),
               names_to = "Beverage_Types",
               values_to = "Litres") %>%
  mutate(Year = as.double(Year)) %>%
  group_by(Beverage_Types,Year) %>%
  na.omit() %>%
  summarise(sum = sum(Litres, na.rm = TRUE))
  
  trend_total %>%
  ggplot(aes(x = Year,
            y = sum,
            group = Beverage_Types,
            color = Beverage_Types)) +
  geom_line(size = 1.5) +
    theme_classic() +
    theme(panel.grid.major.x = element_blank(), 
          axis.ticks.y = element_blank(),
          legend.position='bottom') +
    scale_color_brewer(palette = "Paired") +
    scale_x_continuous(breaks=seq(1960, 2020, 5)) 
```

### Research Question 1 

**How has the popularity of each type of alcohol changed over the years for different countries and have the local favorites of earlier decades been overtaken by other types of alcohol in terms of consumption?**


Cause of Mortality {.tabset}
======================

Column {.tabset} {data-width=650}
-------------------------------------

```{r}
alcohol_cancer <- read.csv("../clean_data/cancer_a_clean.csv")
alcohol_liver <- read.csv("../clean_data/liver_a_clean.csv")
alcohol_traffic <- read.csv("../clean_data/traffic_a_clean.csv")
death_cancer <- read.csv("../clean_data/cancer_d_clean.csv")
death_liver <- read.csv("../clean_data/liver_d_clean.csv")
death_traffic <- read.csv("../clean_data/traffic_d_clean.csv")

alc_cancer_death <- death_cancer %>%
  left_join(alcohol_cancer) %>% 
  mutate(can_alc_death = `cancer.death.population` * `alc.attri.death.cancer`/100) %>% 
  select(Country, gender, can_alc_death)
  
alc_liver_death <- death_liver %>%
  left_join(alcohol_liver) %>% 
  mutate(liver_alc_death = `liver.cirrhosis.death.population` * `alc.attri.death.liver`/100) %>% 
    select(Country, gender, liver_alc_death)

alc_traffic_death <- death_traffic %>%
  left_join(alcohol_traffic) %>% 
  mutate(`alc.attri.death.traffic` = as.numeric(`alc.attri.death.traffic`)) %>% 
    mutate(traffic_alc_death = `road.traffic.death.population` * `alc.attri.death.traffic`/100) %>% 
  select(Country, gender, traffic_alc_death)    

 alc_death <- alc_cancer_death %>% 
  left_join(alc_liver_death) %>% 
  left_join(alc_traffic_death) %>% 
  pivot_longer(cols = c("can_alc_death", "liver_alc_death", "traffic_alc_death"),
               names_to = "cause_of_death",
               values_to = "number_of_death") 

```

### Overview on the alcohol-attributed death

```{r}

countries <- ne_countries(returnclass = "sf", scale = "medium") %>%
  select(admin, continent, income_grp)

 alc_death_sum <- alc_death %>% 
   group_by(Country) %>% 
   summarise(number_of_death = sum(number_of_death))

map_all <- alc_death_sum %>%
  mutate(Country = recode(Country,
                             "Bahamas" = "The Bahamas",
                             "Bolivia (Plurinational State of)" = "clean.htmlBolivia",
                             "Brunei Darussalam" = "Brunei",
                             "Cabo Verde" = "Cape Verde",
                             "Congo" = "Democratic Republic of the Congo",
                             "Czechia" = "Czech Republic",
                             "Democratic People's Republic of Korea" = "North Korea",
                             "Guinea-Bissau" = "Guinea Bissau",
                             "Iran (Islamic Republic of)" = "Iran",
                             "Lao People's Democratic Republic" = "Laos",
                             "Micronesia (Federated States of)" = "Federated States of Micronesia",
                             "North Macedonia" = "Macedonia",
                             "Republic of Korea" = "South Korea",
                             "Republic of Moldova" = "Moldova",
                             "Russian Federation" = "Russia",
                             "Serbia" = "Republic of Serbia",
                             "Syrian Arab Republic" = "Syria",
                             "Timor-Leste" = "East Timor",
                             "United Kingdom of Great Britain and Northern Ireland" = "United Kingdom", 
                             "Venezuela (Bolivarian Republic of)" = "Venezuela",
                             "Viet Nam" = "Vietnam")) 

all_loc <-left_join(countries, map_all, by = c("admin" = "Country"))
world_points<- st_centroid(all_loc)
world_points <- cbind(all_loc, st_coordinates(st_centroid(all_loc$geometry)))

p1 <- all_loc %>% 
      ggplot()+
  geom_sf(mapping = aes(fill = number_of_death))+
  geom_text(data= world_points,aes(x=X, y=Y, label=admin),
    color = "transparent", size = 1, check_overlap = FALSE)+
  scale_fill_distiller(palette = "Spectral", na.value = "white", )+
  labs(title = "Overview on number of alcohol-attributed deaths(per 100,000 population)",
       fill = "") +
  theme_void()+
  theme(panel.grid.major = element_line(colour = "transparent"),
        legend.position = "bottom")

ggplotly(p1)

```

### Comparison between alcohol-attributed deaths

**Calculation Method:**

- Cancer Death $\times$ Alcohol-Attributed Cancer Death Rate

- Liver Cirrhosis Death $\times$ Alcohol-attributed Liver Cirrhosis Death Rate

- Road Traffic Death $\times$ Alcohol-attributed Road Traffic Death Rate

- Sum up all types of alcohol-attributed deaths


**Analysis:**

- Alcohol causes the highest death rate in *Nigeria* and the lowest in *Lybia*.

- Alcohol brings the highest number of deaths in African countries while the lowest in Middle East countries.

- Alcohol causes more deaths to *Males*.

- *Liver Cirrhosis* causes the highest death rate while *Road Traffic Accidents* causes the lowest.

**Possible reasons affecting death rates**

- Religions

- Income

- Education




Column {.tabset} {data-width=350}
-------------------------------------

### Total number of alcohol attributed death

```{r fig.height=4 ,fig.width=2}

overview <- alc_death %>% 
  group_by(gender, cause_of_death) %>%  
  ggplot(aes(x = cause_of_death,
             y = number_of_death,
             fill = gender))+
    geom_col(position = "dodge")+
    theme_bw() 
ggplotly(overview)

```

### Alcohol-Attributed Death VS Road Traffic death (By Income Level)

```{r }

alc_death %>%
  left_join(countries, by = c("Country" = "admin")) %>% 
  mutate(income_grp = recode(income_grp,
                            `2. High income: nonOECD` = "high",
                            `5. Low income` = "low",
                            `3. Upper middle income` =  "upper_middle",
                            `4. Lower middle income` =  "lower_middle",
                            `1. High income: OECD` = "high")) %>%
  group_by(Country, income_grp, gender) %>%
  summarise(alc_death = sum(number_of_death)) %>% 
  left_join(death_traffic) %>% 
  drop_na() %>% 
  rename("traffic_death" = `road.traffic.death.population`) %>% 
    group_by(income_grp) %>% 
  summarise(alc_death = mean(alc_death),
            traffic_death = mean(traffic_death))%>%    
  arrange(desc(alc_death)) %>%
  kable(align = "c", col.names = c("income group",
                           "alcohol-attribute death", "road traffic death")) %>% 
  kable_styling("striped","hover")
  
```

### Comparison between total alcohol-attributed deaths and traffic deaths

**Harms of alcohol**

- Cancer

- Liver Cirrhosis

- Road traffic accidents

**Calculation method: **

- Average number of deaths(per 100,000 population) in each continent.


**Analysis:**

- Alcohol causes more deaths to *Males*.

- *Liver Cirrhosis* causes the highest death rate while *Road Traffic Accidents* causes the lowest.


Policy Pattern {.tabset}
======================

Column {.tabset} {data-width = 400}
------------------------
### Infographic of Policies

```{r read_data}
policy_pattern <- read_csv("../clean_data/policy_pattern.csv")
consumption_pattern <- read_csv("../clean_data/consumption_pattern.csv")
```

```{r}

policy_country_group <- policy_pattern %>%
  pivot_longer(cols = c("2010", "2011", "2012", "2013", "2014","2015", "2016"),
               names_to = "Year",
               values_to = "Action")

cities <- data.frame(world.cities) %>%
  filter(capital == 1)

world <- map_data("world") %>%
  mutate(Country = region) %>%
  select(long,lat,region)

policy_country_group_map <- policy_country_group %>%
  left_join(cities, by = c("Country" = "country.etc")) %>%
  na.omit() %>%
  select(Country,`Action Area`,Action,lat,long,name,Year)
```

```{r}
ui <- bootstrapPage(tags$style(type = "text/css", "html, body, .leaflet {width:100%; height:100%}"),
                    leafletOutput("map", width = "100%", height = "100%"),
                    # position and properties of the time slider
                    absolutePanel(top = 10, right = 10, draggable = TRUE,
                                  # slider title, step increments, and ticks
                                  sliderInput("integer", "Year", min = 2010, max = 2016, value = 2010, step = 1,ticks = FALSE, width = '100px', sep = "",
                                              animate =
                                                  animationOptions(interval = 4000, loop = TRUE))))

# shiny server input/output
server <- function(input, output, session) {
    filteredData <- reactive({
        policy_country_group_map %>%
            filter(Year == input$integer)
    })
    output$map <- renderLeaflet({
        leaflet(world) %>%
            addProviderTiles(providers$CartoDB.Positron) %>%
            # set boundaries for map
            fitBounds(lng1 = min(world$long),
                      lat1 = min(world$lat),
                      lng2 = max(world$long),
                      lat2 = max(world$lat))
    })
    observe({
        leafletProxy("map", data = filteredData()) %>%
            clearMarkers() %>%
            addMarkers(~long, ~lat, popup = ~as.character(Action), label = ~as.character(`Action Area`))
    })
}
shinyApp(ui=ui, server=server, options = list(height = 500), enableBookmarking = "server")
```


### Effectiveness of Policy Actions

```{r}
consumption_pattern_filter <- consumption_pattern %>%
  filter(`Beverage Types` == "All types") %>%
  select(-`Beverage Types`) %>%
  pivot_longer(cols = -c("Country"), names_to = "Year", values_to = "Per Capita Alcohol Consumed") %>%
  left_join(policy_country_group) %>%
  filter(`Per Capita Alcohol Consumed` > 0) %>%
  group_by(Country) %>%
  arrange(Year, .by_group = TRUE)

df <- data.frame(row_no=numeric())
consumption_pattern_filter$row_no <- seq.int(nrow(consumption_pattern_filter)) 

finaltbl <- consumption_pattern_filter %>%
  na.omit() %>%
  mutate(row_no2 = row_no + 1)

addtbl <- finaltbl %>%
  select(row_no2) %>%
  left_join(consumption_pattern_filter) %>%
  filter(row_no == row_no2) %>%
  select(-c(row_no,row_no2))

finaltbl <- finaltbl %>%
  select(-c(row_no,row_no2))
  

tbl1 <- rbind(addtbl,finaltbl) %>%
  arrange(Country, Year)

tbl <- tbl1 %>%
  distinct(`Per Capita Alcohol Consumed`, .keep_all = TRUE) %>%
  select(Year, `Per Capita Alcohol Consumed`)

```



```{r}

lag_tbl <- lag(tbl) %>%
  select(Country, Year, `Per Capita Alcohol Consumed`) %>%
  mutate(alc_diff = `Per Capita Alcohol Consumed`) %>%
  cbind(tbl) %>%
   transmute(Country = Country...5, Year = Year...6, `Per Capita Alcohol Consumed` = `Per Capita Alcohol Consumed...7`,alc_diff = alc_diff)
 for (i in 1:452) {
   ifelse(lag_tbl$Country[i] == lag_tbl$Country[i+1],
          next,
          lag_tbl$alc_diff[i+1] <- NA)
 }
lag_tbl <- lag_tbl %>%
  mutate(Year = as.numeric(Year)-1)

lag_tbl <- lag_tbl %>%
   mutate(alc_diff_2= (`Per Capita Alcohol Consumed` - alc_diff)/alc_diff*100) %>%
   filter(!is.na(alc_diff_2)) %>%
   mutate(Trend = ifelse(alc_diff_2<=0,"Reducing","Increasing"))

tbl1 <- tbl1 %>%
  mutate(Year = as.numeric(Year)) %>%
  select(-`Per Capita Alcohol Consumed`)

check_tbl <- full_join(lag_tbl,tbl1) %>%
  arrange(Country, Year) %>%
  na.omit() %>%
  unique()

fin_tbl <- check_tbl %>%
   group_by(Year,`Action Area`, Trend) %>%
   tally() %>%
  mutate(Year = as.character(Year))

p2 <- fin_tbl %>%
  ggplot(aes(y = Year, x= n,fill = Trend)) +
  facet_wrap(~`Action Area`, labeller = labeller(`Action Area` = label_wrap_gen(70)), ncol = 2) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(strip.background = element_rect(colour = "white", fill = "white"), strip.text.x = element_text(size=6, color = "black", face = "bold"), axis.text.y = element_text(angle = 5, hjust = 1, size = 6), axis.title.x = element_text(size=9)) +
  labs(x = "Number of Countries")

ggplotly(p2)
```



Column {.tabset} {data-width = 650}
------------------------------------

### Policies being favored by countries across years 2010-2016

```{r}
policy_country_group_plot <- check_tbl %>%
  na.omit() %>%
  group_by(`Action Area`,Year) %>%
  tally() %>%
  arrange(Year)


p <- policy_country_group_plot %>%
  ggplot(aes(x=Year,y=n, group = `Action Area`)) +
  geom_line(aes(color = `Action Area`)) +
  geom_point() +
  labs(y = "Number of Countries") +
  theme_bw() +
  theme(legend.position = "left", legend.text = element_text(size = 7)) 
ggplotly(p) %>%
  layout(legend = list(x = 0,
                     y = 1,
                     tracegroupgap = 0))
```



### Analysis

```{r}
act_area <-  length(unique(policy_country_group$`Action Area`))
```

- There are `r act_area` main areas of Policy Actions that the effectiveness are measured for.
From the figure of Policies favored across countries from the years 2010-2016, it is visible that 'Leadership, awareness and commitment' policies are the ones that are being favored by most countries.
```{r}
df <- check_tbl %>%
  arrange(alc_diff_2)
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally() %>%
  length()
```

- Upon checking the largest percentage decrease in per capita alcohol consumption it is visible that this policy has only `r df` entry which has resulted in a decrease.
```{r}
df <- check_tbl %>%
  arrange(desc(alc_diff_2))
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally()
```

- However upon checking the largest percentage increase in per capita alcohol consumption it is visible that this policy has `r df[1]` entries.
- This shows that the governments are not taking the efficient route.
```{r}
df <- check_tbl %>%
  group_by(`Action Area`) %>%
  summarise(mean = mean(alc_diff_2)) %>%
  arrange(mean)

kbl(df) %>%
  kable_minimal(font_size = 9) %>%
  row_spec(1, bold = T) %>%
  row_spec(10, bold = T)
```
- From the table we can see that the most efficient action area seems to be - `r paste(df$'Action Area'[1])`
- While the least efficient area is - `r paste(df$'Action Area'[10])`
- One area of relief is that the second most efficent action area i.e., `r paste(df$'Action Area'[2])`, is also the second most used strategy by countries across the world.
```{r}
df1 <- check_tbl %>%
  filter(alc_diff_2 == min(alc_diff_2))
df2 <- check_tbl %>%
  filter(alc_diff_2 == max(alc_diff_2))
```

> The biggest dip in consumption was seen in `r paste(df1$Country[1])` in the year `r paste(df1$Year[1])` after the step - `r paste(df1$Action[1])` The policy area for this is - `r paste(df1$'Action Area'[1])`. There was a dip in consumption by `r paste(df1$alc_diff_2[1])`%.

> The biggest spike in consumption was seen in `r paste(df2$Country[1])` in the year `r paste(df2$Year[1])` within the policy area - `r paste(df2$'Action Area'[1])`. There was a spike in consumption by `r paste(df2$alc_diff_2[1])`%. Bhutan's alcoholism is an issue that has been noted and despite efforts there seems to be no solution yet.

-------------------

Age Restrictions {.tabset}
======================

```{r}
BAC_limits_tidy <- read_csv(here::here("clean_data/BAC_limits_tidy.csv"))
Age_limits_tidy <- read_csv(here::here("clean_data/Age_limits_tidy.csv"))
current_drinkers_15_19_tidy <- read_csv(here::here("clean_data/current_drinkers_15_19_tidy.csv"))
heavy_drinkers_15_19_tidy <- read_csv(here::here("clean_data/heavy_drinkers_15_19_tidy.csv"))
```

```{r}
limits <- BAC_limits_tidy %>% 
  left_join(Age_limits_tidy) %>% 
  left_join(current_drinkers_15_19_tidy) %>% 
  left_join(heavy_drinkers_15_19_tidy) %>% 
  rename("Age_limit" = limit)
limits1 <- limits %>% 
  mutate(Age_limit = tolower(Age_limit),
         BAC_limits = tolower(BAC_limits)) %>% 
  filter(gender == "All") %>% 
  filter(!str_detect(Age_limit, "no data"),
         !str_detect(Service, "service")) %>% 
  mutate(Age_limit = ifelse(Age_limit == "total ban", "99", Age_limit), 
         Age_limit = ifelse(Age_limit == "none", "0", Age_limit),
         Age_limit = ifelse(Age_limit == "subnational", "18", Age_limit)) %>% 
  mutate(Age_limit = as.numeric(Age_limit)) %>% 
  mutate(country = ifelse(country == "Russian Federation", "Russia", country),
         country = ifelse(country == "Iran (Islamic Republic of)", "Iran", country),
         country = ifelse(country == "United States of America", "USA", country),
         country = ifelse(country == "Venezuela (Bolivarian Republic of)", "Venezuela", country),
         country = ifelse(country == "Viet Nam", "Vietnam", country),
         country = ifelse(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country),
         country = ifelse(country == "Czechia", "Czech Republic", country),
         country = ifelse(country == "Congo", "Democratic Republic of the Congo", country),
         country = ifelse(country == "United Republic of Tanzania", "Tanzania", country))

limits2 <- limits1 %>% 
  group_by(country) %>% 
  summarise(Age_limit = min(Age_limit)) 
  
limits_tidy <- limits1 %>% 
  select(country, BAC_limits, drinker_percentage, heavy_drinker_percentage) %>% 
  group_by(country) %>% 
  distinct() %>% 
  full_join(limits2) %>% 
  mutate(BAC_limits = factor(BAC_limits, 
                            levels = c("none", "0.08%", "0.07%", "0.06%", "0.05%", "0.04%", "0.03%", "0.02%", "0.01%", "zero tolerance", "total ban"))) %>% 
  mutate(Age_limit = factor(Age_limit, 
                            levels = as.character(c("0", "16", "17", "18", "20", "21", "25", "99")))) %>% 
  rename("drinker_rate" = drinker_percentage,
         "heavy_rate" = heavy_drinker_percentage)
```

Column {data-width=650}
---------------------------


### table


```{r}
limits_tidy %>% 
  ungroup() %>%
  summarise(mean_drinker_rate = mean(drinker_rate),
            mean_heavy_rate = mean(heavy_rate)) %>% 
  kable(caption = "Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```



### map

```{r}
world_map <- map_data("world") %>%
  right_join(limits_tidy, 
            by = c("region" = "country")) %>%
  select(-subregion)
worldMaps <- function(data_type){
if(data_type == "drinker_rate") 
  {
  p <- world_map %>%
  ggplot(aes(x = long, 
             y = lat, 
             group = group,
             text = region)) +
  geom_polygon(aes(fill = drinker_rate), 
               colour = "gray50") +
  scale_x_continuous(breaks = seq(-180, 210, 45)) +
  scale_y_continuous(breaks = seq(-60, 100, 30)) +
  labs(x = "Longitude", 
       y = "Latitude") +
  theme_light()
  
  
}
  else if(data_type == "heavy_rate") {
    
  p <- world_map %>%
  ggplot(aes(x = long, 
             y = lat, 
             group = group,
             text = region)) +
  geom_polygon(aes(fill = heavy_rate), 
               colour = "gray50") +
  scale_x_continuous(breaks = seq(-180, 210, 45)) +
  scale_y_continuous(breaks = seq(-60, 100, 30)) +
  labs(x = "Longitude", 
       y = "Latitude") +
  theme_light()
  
  
  }
  else if(data_type == "BAC_limits") {
    
  p <- world_map %>%
  ggplot(aes(x = long, 
             y = lat, 
             group = group,
             text = region)) +
  geom_polygon(aes(fill = BAC_limits), 
               colour = "gray50") +
  scale_x_continuous(breaks = seq(-180, 210, 45)) +
  scale_y_continuous(breaks = seq(-60, 100, 30)) +
  labs(x = "Longitude", 
       y = "Latitude") +
  theme_light()
  
  }
  else {
    
  p <- world_map %>%
  ggplot(aes(x = long, 
             y = lat, 
             group = group,
             text = region)) +
  geom_polygon(aes(fill = Age_limit), 
               colour = "gray50") +
  scale_x_continuous(breaks = seq(-180, 210, 45)) +
  scale_y_continuous(breaks = seq(-60, 100, 30)) +
  labs(x = "Longitude", 
       y = "Latitude") +
  theme_light()
  }
  return(p)
  #ggplotly(p)
}
```


```{r}
ui <- fluidPage(
    selectInput("variable", "Variable:",
                c("drinker_rate" = "drinker_rate", "heavy_rate" = "heavy_rate", "Age_limit" = "Age_limit", "BAC_limits" = "BAC_limits")),
    mainPanel(plotOutput(outputId = "plot_output"))
  )
server <- function(input,output,session) {
    output$plot_output <- renderPlot({
      worldMaps(input$variable)
    })
  }
shinyApp(ui=ui, server=server, options = list(height = 500), enableBookmarking = "server")
```





Column {data-width=350}
---------------------------


### Analysis
  
* Based on 15-19 years old adolescents  
* Youth drinker mean percentage across world: 31.2%  
* Youth heavy drinker mean percentage  
(Based on drinkers) across world: 48.5%  
* Roughly high rate  
  
    
    
* Low rate of drinkers:  
**The Middle East** & **North Africa**    
  
* High rate of drinkers:  
**USA** & **Argentina** & **Australia** & **European countries** 
  
* Possible reasons:  
  + Low rate   
    - Age restriction: "Total Ban"   
    - Religion: Islam (Alcohol Forbidden)  
  + High rate
    - Rich drinking culture
    - Rich in wine
      
* Low rate of heavy drinkers: 
**The Middle East** & **North Africa**     
    
* High rate of heavy drinkers:  
**Russia** & **West Africa**
   
* Possible reasons:    
  + Low rate 
    - Same as above   
  + High rate  
    - BAC restriction: more relaxed  
    - Economic depression  
    - Drinking culture  
    - National character  
    - Natural cold  




Youth Inebriation {.tabset}
======================

```{r}
at_least_once_a_week_tidy <- read_csv(here::here("clean_data/at_least_once_a_week_tidy.csv"))
first_drink_earlier_than_13_tidy <- read_csv(here::here("clean_data/first_drink_earlier_than_13_tidy.csv"))
any_alcohol_in_past_12_months_tidy <- read_csv(here::here("clean_data/any_alcohol_in_past_12_months_tidy.csv"))
any_alcohol_in_past_30_days_tidy <- read_csv(here::here("clean_data/any_alcohol_in_past_30_days_tidy.csv"))
```

```{r}
youth_drinking1 <- first_drink_earlier_than_13_tidy %>% 
  filter(!gender == "All") %>% 
  full_join(at_least_once_a_week_tidy, 
            by = c("country", "year", "gender")) %>% 
  rename("first_drink_earlier_than_13_percentage" = percentage.x,
         "at_least_once_a_week_percentage" = percentage.y) %>% 
  filter(!is.na(first_drink_earlier_than_13_percentage),
         !is.na(at_least_once_a_week_percentage)) %>% 
  group_by(country, gender) %>%
  summarise(first_drink_earlier_than_13_mean = mean(first_drink_earlier_than_13_percentage),
            at_least_once_a_week_mean = mean(at_least_once_a_week_percentage))

```


```{r}
youth_drinking2 <- any_alcohol_in_past_12_months_tidy %>% 
  filter(!str_detect(gender, "All"),
         !is.na(percentage)) %>% 
  group_by(country, gender) %>% 
  summarise(any_alcohol_in_past_12_months_mean = mean(percentage))

youth_drinking3 <- any_alcohol_in_past_30_days_tidy %>% 
  filter(!str_detect(gender, "All"),
         !is.na(percentage)) %>% 
  group_by(country, gender) %>% 
  summarise(any_alcohol_in_past_30_days_mean = mean(percentage))
```

```{r}
youth_drinking <- youth_drinking1 %>% 
  left_join(youth_drinking2) %>%
  left_join(youth_drinking3) %>% 
  filter(!is.na(any_alcohol_in_past_12_months_mean),
         !is.na(any_alcohol_in_past_30_days_mean)) %>% 
  select(-first_drink_earlier_than_13_mean) %>% 
  pivot_longer(cols = -c(country, gender),
               names_to = "frequency",
               values_to = "percentage") %>%
  mutate(country = ifelse(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country),
         country = ifelse(country == "United States of America", "USA", country),
         country = ifelse(country == "Russian Federation", "Russia", country))

youth_drinking$frequency <- factor(youth_drinking$frequency, levels = c("at_least_once_a_week_mean", "any_alcohol_in_past_30_days_mean", "any_alcohol_in_past_12_months_mean"))
```

Column 
---------------------------

### Barplot

```{r, fig.height=6}
freq <- youth_drinking %>% 
  ggplot(aes(x = percentage,
             y = reorder(country, desc(percentage)),
             fill = gender,
             text = country)) +
  geom_col() +
  facet_grid(~frequency, scales = "free_x") +
  theme_bw() + 
  scale_fill_brewer(palette = "Paired")

ggplotly(freq)
```

  
 


### Analysis  
  
* Based on 15-year-old adolescents & mainly based in Europe  
* Low frequency:  
**Northern Europe**  
* High frequency:  
**Malta** & **Czech** & **Denmark** & **Austria** etc.    
* Possible reasons:  
  + Good taste   
  + Low price   
* Examples: (According to a European study *ESPAD*)       
  + Danish children: most enthusiastic drinkers  
  + Icelandic teenagers: not being attracted to addictive substances  



Limitations {.tabset} 
======================

Column {.tabset}
---------------------------
### Popularity

### Cause of Mortality

1. There can be unidentified alcohol-attributed deaths.
2. It contains only 2016 data that may cause limitations in explaining the situation.
3. There are missing data in some areas that would affect the accuracy of the analysis.

### Policy Patterns

1. The values for each policy area have not been weighted by importance.
2. Data is not available for a large number of countries so the analysis has been performed on the limited data set given.
3. This analysis has only been limited between the years of 2010-2016.
4. There could be population/age bias as demographic data is unavailable.



### Age Restrictions

1. Only data in 2016 is included in the dataset.
2. There are several countries with NAs in either age or BAC limits.  
3. Many other factors affect adolescent drinking.  

### Youth Inebriation

1. Only 15-year-olds were analyzed.  
2. Each set of data has only a few years.  
3. Only part of countries are included in dataset.


References {.tabset}
======================

GHO | global information system on alcohol and Health (gisah) | global information system on alcohol and health. (n.d.). Retrieved May 09, 2021, from https://apps.who.int/gho/data/node.gisah.GISAH?lang=en&amp;showonly=GISAH

Need to control alcohol consumption. (2017, January 24). Retrieved May 15, 2021, from https://kuenselonline.com/need-to-control-alcohol-consumption/

Writer, S. (2019, August 10). South Africa has some of the heaviest drinkers in the world. Retrieved May 20, 2021, from https://businesstech.co.za/news/lifestyle/332909/south-africa-has-some-of-the-heaviest-drinkers-in-the-world/

(www.dw.com), D. W. (2015, January 05). Tanzania mulls action on alcohol misuse: DW: 05.01.2015. Retrieved May 20, 2021, from https://www.dw.com/en/tanzania-mulls-action-on-alcohol-misuse/a-18171168

Meltzer, M. (2019, March 18). Your guide to drinking laws in the Arab world. Retrieved May 20, 2021, from https://matadornetwork.com/read/drinking-laws-arab-world/

Drucker, D. P., Mutumbuka, D., & V, G. (2015, November 26). Literacy & the Economy. Retrieved May 20, 2021, from http://www.read.org.za/useful-info/literacy-the-economy/
