---
title: "Alcohol Consumption Patterns"
output:
  flexdashboard::flex_dashboard:
    theme: bootstrap
<<<<<<< HEAD
    vertical_layout: scroll
runtime: shiny
=======
    orientation: columns
    vertical_layout: scroll
    runtime: shiny
>>>>>>> 08f5d35 (Map and boxplot)
---
   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(maps)
library(plotly)
library(flexdashboard)
library(kableExtra)
<<<<<<< HEAD
library(leaflet)
library(stringr)
=======
>>>>>>> 08f5d35 (Map and boxplot)
library(shiny)
library(gridExtra)
library(ggiraph)
```

Introduction {.tabset}
======================

Column {.tabset} {data-width=800}
-------------------------------------

### Background




Column {.tabset} {data-width=200}
-------------------------------------

### Approach of Project

The report will be collating specific sections of this data pertaining to countrywise policy responses, consumption pattern, youth and alcohol, levels of consumption and harms and consequences.

### Information on Data

This report is being created using the data from the GISAH (Global Information System on Alcohol and Health) tool of the World Health Organisation. GISAH tool helps monitor trends relating to alcohol consumption across various age groups, side effects (harm caused) as well as the policy responses by different countries.

### Makers

**Team Name: Hayaku**

_Researchers:_

- _Kexin Xu_
- _Smriti Vinayak Bhat_
- _Yalong liu_
- _Yin Shan Ho_


Popularity {.tabset} 
======================


Cause of Mortality {.tabset} 
======================

Policy Pattern {.tabset}
======================

Column {.tabset} {data-width = 400}
------------------------
### Infographic of Policies

```{r read_data}
policy_pattern <- read_csv("../clean_data/policy_pattern.csv")
consumption_pattern <- read_csv("../clean_data/consumption_pattern.csv")
```

```{r}

policy_country_group <- policy_pattern %>%
  pivot_longer(cols = c("2010", "2011", "2012", "2013", "2014","2015", "2016"),
               names_to = "Year",
               values_to = "Action")

cities <- data.frame(world.cities) %>%
  filter(capital == 1)

world <- map_data("world") %>%
  mutate(Country = region) %>%
  select(long,lat,region)

policy_country_group_map <- policy_country_group %>%
  left_join(cities, by = c("Country" = "country.etc")) %>%
  na.omit() %>%
  select(Country,`Action Area`,Action,lat,long,name,Year)
```

```{r}
ui <- bootstrapPage(tags$style(type = "text/css", "html, body, .leaflet {width:100%; height:100%}"),
                    leafletOutput("map", width = "100%", height = "100%"),
                    # position and properties of the time slider
                    absolutePanel(top = 10, right = 10, draggable = TRUE,
                                  # slider title, step increments, and ticks
                                  sliderInput("integer", "Year", min = 2010, max = 2016, value = 2010, step = 1,ticks = FALSE, width = '100px', sep = "",
                                              animate =
                                                  animationOptions(interval = 4000, loop = TRUE))))

# shiny server input/output
server <- function(input, output, session) {
    filteredData <- reactive({
        policy_country_group_map %>%
            filter(Year == input$integer)
    })
    output$map <- renderLeaflet({
        leaflet(world) %>%
            addProviderTiles(providers$CartoDB.Positron) %>%
            # set boundaries for map
            fitBounds(lng1 = min(world$long),
                      lat1 = min(world$lat),
                      lng2 = max(world$long),
                      lat2 = max(world$lat))
    })
    observe({
        leafletProxy("map", data = filteredData()) %>%
            clearMarkers() %>%
            addMarkers(~long, ~lat, popup = ~as.character(Action), label = ~as.character(`Action Area`))
    })
}
shinyApp(ui=ui, server=server, options = list(height = 500), enableBookmarking = "server")
```


### Effectiveness of Policy Actions

```{r}
consumption_pattern_filter <- consumption_pattern %>%
  filter(`Beverage Types` == "All types") %>%
  select(-`Beverage Types`) %>%
  pivot_longer(cols = -c("Country"), names_to = "Year", values_to = "Per Capita Alcohol Consumed") %>%
  left_join(policy_country_group) %>%
  filter(`Per Capita Alcohol Consumed` > 0) %>%
  group_by(Country) %>%
  arrange(Year, .by_group = TRUE)

df <- data.frame(row_no=numeric())
consumption_pattern_filter$row_no <- seq.int(nrow(consumption_pattern_filter)) 

finaltbl <- consumption_pattern_filter %>%
  na.omit() %>%
  mutate(row_no2 = row_no + 1)

addtbl <- finaltbl %>%
  select(row_no2) %>%
  left_join(consumption_pattern_filter) %>%
  filter(row_no == row_no2) %>%
  select(-c(row_no,row_no2))

finaltbl <- finaltbl %>%
  select(-c(row_no,row_no2))
  

tbl1 <- rbind(addtbl,finaltbl) %>%
  arrange(Country, Year)

tbl <- tbl1 %>%
  distinct(`Per Capita Alcohol Consumed`, .keep_all = TRUE) %>%
  select(Year, `Per Capita Alcohol Consumed`)

```



```{r}

lag_tbl <- lag(tbl) %>%
  select(Country, Year, `Per Capita Alcohol Consumed`) %>%
  mutate(alc_diff = `Per Capita Alcohol Consumed`) %>%
  cbind(tbl) %>%
   transmute(Country = Country...5, Year = Year...6, `Per Capita Alcohol Consumed` = `Per Capita Alcohol Consumed...7`,alc_diff = alc_diff)
 for (i in 1:452) {
   ifelse(lag_tbl$Country[i] == lag_tbl$Country[i+1],
          next,
          lag_tbl$alc_diff[i+1] <- NA)
 }
lag_tbl <- lag_tbl %>%
  mutate(Year = as.numeric(Year)-1)

lag_tbl <- lag_tbl %>%
   mutate(alc_diff_2= (`Per Capita Alcohol Consumed` - alc_diff)/alc_diff*100) %>%
   filter(!is.na(alc_diff_2)) %>%
   mutate(Trend = ifelse(alc_diff_2<=0,"Reducing","Increasing"))

tbl1 <- tbl1 %>%
  mutate(Year = as.numeric(Year)) %>%
  select(-`Per Capita Alcohol Consumed`)

check_tbl <- full_join(lag_tbl,tbl1) %>%
  arrange(Country, Year) %>%
  na.omit() %>%
  unique()

fin_tbl <- check_tbl %>%
   group_by(Year,`Action Area`, Trend) %>%
   tally() %>%
  mutate(Year = as.character(Year))

p2 <- fin_tbl %>%
  ggplot(aes(y = Year, x= n,fill = Trend)) +
  facet_wrap(~`Action Area`, labeller = labeller(`Action Area` = label_wrap_gen(70)), ncol = 2) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(strip.background = element_rect(colour = "white", fill = "white"), strip.text.x = element_text(size=6, color = "black", face = "bold"), axis.text.y = element_text(angle = 5, hjust = 1, size = 6), axis.title.x = element_text(size=9)) +
  labs(x = "Number of Countries")

ggplotly(p2)
```



Column {.tabset} {data-width = 650}
------------------------------------

### Policies being favored by countries across years 2010-2016

```{r}
policy_country_group_plot <- check_tbl %>%
  na.omit() %>%
  group_by(`Action Area`,Year) %>%
  tally() %>%
  arrange(Year)


p <- policy_country_group_plot %>%
  ggplot(aes(x=Year,y=n, group = `Action Area`)) +
  geom_line(aes(color = `Action Area`)) +
  geom_point() +
  labs(y = "Number of Countries") +
  theme_bw() +
  theme(legend.position = "left", legend.text = element_text(size = 7)) 
ggplotly(p) %>%
  layout(legend = list(x = 0,
                     y = 1,
                     tracegroupgap = 0))
```



### Analysis

```{r}
act_area <-  length(unique(policy_country_group$`Action Area`))
```

- There are `r act_area` main areas of Policy Actions that the effectiveness are measured for.
From the figure of Policies favored across countries from the years 2010-2016, it is visible that 'Leadership, awareness and commitment' policies are the ones that are being favored by most countries.
```{r}
df <- check_tbl %>%
  arrange(alc_diff_2)
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally() %>%
  length()
```

- Upon checking the largest percentage decrease in per capita alcohol consumption it is visible that this policy has only `r df` entry which has resulted in a decrease.
```{r}
df <- check_tbl %>%
  arrange(desc(alc_diff_2))
df <- head(df,10) %>%
  filter(str_detect(`Action Area`,"Leadership")) %>%
  tally()
```

- However upon checking the largest percentage increase in per capita alcohol consumption it is visible that this policy has `r df[1]` entries.
- This shows that the governments are not taking the efficient route.
```{r}
df <- check_tbl %>%
  group_by(`Action Area`) %>%
  summarise(mean = mean(alc_diff_2)) %>%
  arrange(mean)

kbl(df) %>%
  kable_minimal(font_size = 9) %>%
  row_spec(1, bold = T) %>%
  row_spec(10, bold = T)
```
- From the table we can see that the most efficient action area seems to be - `r paste(df$'Action Area'[1])`
- While the least efficient area is - `r paste(df$'Action Area'[10])`
- One area of relief is that the second most efficent action area i.e., `r paste(df$'Action Area'[2])`, is also the second most used strategy by countries across the world.
```{r}
df1 <- check_tbl %>%
  filter(alc_diff_2 == min(alc_diff_2))
df2 <- check_tbl %>%
  filter(alc_diff_2 == max(alc_diff_2))
```

> The biggest dip in consumption was seen in `r paste(df1$Country[1])` in the year `r paste(df1$Year[1])` after the step - `r paste(df1$Action[1])` The policy area for this is - `r paste(df1$'Action Area'[1])`. There was a dip in consumption by `r paste(df1$alc_diff_2[1])`%.

> The biggest spike in consumption was seen in `r paste(df2$Country[1])` in the year `r paste(df2$Year[1])` within the policy area - `r paste(df2$'Action Area'[1])`. There was a spike in consumption by `r paste(df2$alc_diff_2[1])`%. Bhutan's alcoholism is an issue that has been noted and despite efforts there seems to be no solution yet.

-------------------

Age Restrictions {.tabset}
======================

```{r}
BAC_limits_tidy <- read_csv(here::here("clean_data/BAC_limits_tidy.csv"))
Age_limits_tidy <- read_csv(here::here("clean_data/Age_limits_tidy.csv"))
current_drinkers_15_19_tidy <- read_csv(here::here("clean_data/current_drinkers_15_19_tidy.csv"))
heavy_drinkers_15_19_tidy <- read_csv(here::here("clean_data/heavy_drinkers_15_19_tidy.csv"))
```

```{r}
limits <- BAC_limits_tidy %>% 
  left_join(Age_limits_tidy) %>% 
  left_join(current_drinkers_15_19_tidy) %>% 
  left_join(heavy_drinkers_15_19_tidy) %>% 
  rename("Age_limit" = limit)
limits1 <- limits %>% 
  mutate(Age_limit = tolower(Age_limit),
         BAC_limits = tolower(BAC_limits)) %>% 
  filter(gender == "All") %>% 
  filter(!str_detect(Age_limit, "no data"),
         !str_detect(Service, "service")) %>% 
  mutate(Age_limit = ifelse(Age_limit == "total ban", "99", Age_limit), 
         Age_limit = ifelse(Age_limit == "none", "0", Age_limit),
         Age_limit = ifelse(Age_limit == "subnational", "18", Age_limit)) %>% 
  mutate(Age_limit = as.numeric(Age_limit)) %>% 
  mutate(country = ifelse(country == "Russian Federation", "Russia", country),
         country = ifelse(country == "Iran (Islamic Republic of)", "Iran", country),
         country = ifelse(country == "United States of America", "USA", country),
         country = ifelse(country == "Venezuela (Bolivarian Republic of)", "Venezuela", country),
         country = ifelse(country == "Viet Nam", "Vietnam", country),
         country = ifelse(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country),
         country = ifelse(country == "Czechia", "Czech Republic", country),
         country = ifelse(country == "Congo", "Democratic Republic of the Congo", country),
         country = ifelse(country == "United Republic of Tanzania", "Tanzania", country))

limits2 <- limits1 %>% 
  group_by(country) %>% 
  summarise(Age_limit = min(Age_limit)) 
  
limits_tidy <- limits1 %>% 
  select(country, BAC_limits, drinker_percentage, heavy_drinker_percentage) %>% 
  group_by(country) %>% 
  distinct() %>% 
  full_join(limits2) %>% 
  mutate(BAC_limits = factor(BAC_limits, 
                            levels = c("none", "0.08%", "0.07%", "0.06%", "0.05%", "0.04%", "0.03%", "0.02%", "0.01%", "zero tolerance", "total ban"))) %>% 
  mutate(Age_limit = factor(Age_limit, 
                            levels = as.character(c("0", "16", "17", "18", "20", "21", "25", "99"))))
```

```{r}
world_map <- map_data("world") %>% 
  right_join(limits_tidy, 
            by = c("region" = "country")) %>% 
  select(-subregion)
worldMaps <- function(df, data_type){
map1 <- df %>% 
  ggplot(aes(x = long, 
             y = lat, 
             group = group,
             text = region)) +
  geom_polygon(aes(fill = data_type), 
               colour = "gray50") +
  scale_x_continuous(breaks = seq(-180, 210, 45)) +
  scale_y_continuous(breaks = seq(-60, 100, 30)) +
  labs(x = "Longitude", 
       y = "Latitude") +
  theme_light() 
ggplotly(map1)}

#worldMaps(world_map, world_map$drinker_percentage)
```

```{r}
ui = fluidPage(
  titlePanel("Youth drinking analysis via map"),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "data_type",
                  label = "Choose the type of data you want to see:",
                  choices = list("drinker_percentage" = "drinker_percentage", "heavy_drinker_percentage" = "heavy_drinker_percentage", "Age_limit" = "Age_limit", "BAC_limits" = "BAC_limits"))
      
    ),
    mainPanel(
      
      # Hide errors
      tags$style(type = "text/css",
                 ".shiny-output-error { visibility: hidden; }",
                 ".shiny-output-error:before { visibility: hidden; }"),
      
      # Output: interactive world map
      girafeOutput("distPlot")
      
    )
  )
)

# Define the server
server = function(input, output, session) {
  
  # Create the interactive world map
  output$distPlot <- renderGirafe({
    ggiraph(code = {print(worldMaps(world_map, input$data_type))})
  })
  
}
shinyApp(ui = ui, server = server)
```

```{r eval = FALSE}
library(bsselectR)
map_plots <- (list(c(map1, map2), full.names = TRUE))

bsselect(map_plots, type = "img", 
         live_search = TRUE, show_tick = TRUE)
```


It is shown in youth drinkers percentage that most countries in the Middle East, as well as some in West Africa, have significantly lower rates of youth drinking than other regions while USA, Argentina, Australia and European countries illustrate roughly high proportion. Most of age restrictions in the Mid East countries like Saudi Arabia, Sudan, Iran are "total ban" which is one reason for less drinkers. However, it is found that there is no clear correlation between age restrictions and drinkers percentage in the rest countries. Readings of the literature found that the countries with significantly lower rates of drinking were all Muslim, which strictly prohibits alcohol. On the contrast, most countries with high drinkers proportion have a rich drinking culture and some are also rich in wine.

Heavy drinkers percentage based on drinkers indicates obvious higher rates in Russia and some African countries. There are several factors that can contribute to alcohol abuse, like economic depression, national character, drinking culture, natural cold etc. BAC restrictions, which are more relaxed in countries in central and western Africa, may also be contributing to the increase in teenage binge drinking.




Youth Inebriation {.tabset}
======================

```{r}
at_least_once_a_week_tidy <- read_csv(here::here("clean_data/at_least_once_a_week_tidy.csv"))
first_drink_earlier_than_13_tidy <- read_csv(here::here("clean_data/first_drink_earlier_than_13_tidy.csv"))
any_alcohol_in_past_12_months_tidy <- read_csv(here::here("clean_data/any_alcohol_in_past_12_months_tidy.csv"))
any_alcohol_in_past_30_days_tidy <- read_csv(here::here("clean_data/any_alcohol_in_past_30_days_tidy.csv"))
```

```{r}
youth_drinking1 <- first_drink_earlier_than_13_tidy %>% 
  filter(!gender == "All") %>% 
  full_join(at_least_once_a_week_tidy, 
            by = c("country", "year", "gender")) %>% 
  rename("first_drink_earlier_than_13_percentage" = percentage.x,
         "at_least_once_a_week_percentage" = percentage.y) %>% 
  filter(!is.na(first_drink_earlier_than_13_percentage),
         !is.na(at_least_once_a_week_percentage)) %>% 
  group_by(country, gender) %>%
  summarise(first_drink_earlier_than_13_mean = mean(first_drink_earlier_than_13_percentage),
            at_least_once_a_week_mean = mean(at_least_once_a_week_percentage))

```


```{r}
youth_drinking2 <- any_alcohol_in_past_12_months_tidy %>% 
  filter(!str_detect(gender, "All"),
         !is.na(percentage)) %>% 
  group_by(country, gender) %>% 
  summarise(any_alcohol_in_past_12_months_mean = mean(percentage))

youth_drinking3 <- any_alcohol_in_past_30_days_tidy %>% 
  filter(!str_detect(gender, "All"),
         !is.na(percentage)) %>% 
  group_by(country, gender) %>% 
  summarise(any_alcohol_in_past_30_days_mean = mean(percentage))
```

```{r}
youth_drinking <- youth_drinking1 %>% 
  left_join(youth_drinking2) %>%
  left_join(youth_drinking3) %>% 
  filter(!is.na(any_alcohol_in_past_12_months_mean),
         !is.na(any_alcohol_in_past_30_days_mean)) %>% 
  select(-first_drink_earlier_than_13_mean) %>% 
  pivot_longer(cols = -c(country, gender),
               names_to = "frequency",
               values_to = "percentage")

youth_drinking$frequency <- factor(youth_drinking$frequency, levels = c("at_least_once_a_week_mean", "any_alcohol_in_past_30_days_mean", "any_alcohol_in_past_12_months_mean"))
```

```{r}
freq <- youth_drinking %>% 
  ggplot(aes(x = percentage,
             y = reorder(country, desc(percentage)),
             fill = gender)) +
  geom_col() +
  facet_grid(~frequency, scales = "free_x") +
  scale_y_discrete(labels = NULL) +
  labs(y = "") +
  theme_bw()

ggplotly(freq)
```


The plots above are based on 15 year-old teenagers. Most of the countries in the data are in Europe as Europe is a region well-known for its wine culture. It is clearly shown that teenagers in Northern Europe drink obvious the least. Take the Czech Republic and Denmark, where drinking frequencies are relatively high, as an example. According to a European study (ESPAD), the Czech Republic is the top drinker in the world, not only because alcoholic drinks taste awesome, but also due to the cheapest price among all drinks, even cheaper than mineral water and Coke. Besides, the study also revealed that Danish children are the most enthusiastic drinkers while Icelandic teenagers are not being attracted to addictive substances.



Limitations {.tabset} 
======================

Column {.tabset}
---------------------------
### Popularity

### Cause of Mortality

### Policy Patterns

1. The values for each policy area have not been weighted by importance.
2. Data is not available for a large number of countries so the analysis has been performed on the limited data set given.
3. This analysis has only been limited between the years of 2010-2016.
4. There could be population/age bias as demographic data is unavailable.



### Age Restrictions

### Youth Inebriation

References {.tabset}
======================

GHO | global information system on alcohol and Health (gisah) | global information system on alcohol and health. (n.d.). Retrieved May 09, 2021, from https://apps.who.int/gho/data/node.gisah.GISAH?lang=en&amp;showonly=GISAH

Need to control alcohol consumption. (2017, January 24). Retrieved May 15, 2021, from https://kuenselonline.com/need-to-control-alcohol-consumption/